---
title: "Video game review report"
author: "Matt Crump"
---


```{r, echo=FALSE, message=FALSE}
#load libraries
library(tidyverse)

#load the data
review_data <- rio::import("data/review_data.csv")

```


## Number of reviews by year

The below histogram shows the number of video game reviews submitted to Amazon by year. From 1999 reviews largely increased year-on-year which is unsurprising given the growth of Amazon and access to the internet. The dataset shows the peak number of reviews was 2015 with a decline from 2016 to 2018. It is likely that this reflects the dataset being incomplete for recent years rather than the number of reviews declining in reality.

```{r, echo= FALSE}
#Get number of reviews per year

reviews_by_year <- review_data %>%
  group_by(year) %>%
  summarize(counts = n())

#ggplot(data = reviews_by_year, mapping = aes(x=year, y=counts))
#ggplot(reviews_by_year, aes(x=year, y=counts))

# plot
ggplot(data = reviews_by_year, mapping = aes(x=year, y=counts))+
  geom_bar(stat= "identity",fill="white",color="black")+
  scale_x_continuous(breaks = 1999:2018)+
  theme(axis.text.x = element_text(angle = 85, vjust = 1, hjust=1))+
  xlab("")+
  ylab("")+
  ggtitle("Number of reviews per year",
          subtitle = "1999 to 2018")+
  theme(
    panel.background = element_rect(fill = "lightgrey",
                                colour = "lightgrey",
                                linewidth = 0.5, linetype = "solid"),
    panel.grid.major=element_line(colour="black",linewidth = .05),
    panel.grid.minor=element_line(colour="lightgrey"))

```









